Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-26 paper.tex
Describing the experiments of the special cases

%In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models. 
%Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
%Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method. In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%. 
%Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively. 
%According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
%On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p.eps}  &
%\includegraphics[scale=0.22]{lr.eps}   &
%\includegraphics[scale=0.22]{svm.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn.eps}  &
%\includegraphics[scale=0.22]{mlp.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
%  models.}
% You should use a log-log scale here to see it more clearly. Besides,
% please say in a comment the script you are using to generate it, we
% are going to need it later on - JJ
%\label{conv2}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_RAE.eps}  &
%\includegraphics[scale=0.22]{lr_RAE.eps}   &
%\includegraphics[scale=0.22]{svm_RAE.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_RAE.eps}  &
%\includegraphics[scale=0.22]{mlp_RAE.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using ReliefAttributeEval.}
%\label{conv2ReliefAttributeEval}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_CFS.eps}  &
%\includegraphics[scale=0.22]{lr_CFS.eps}   &
%\includegraphics[scale=0.22]{svm_CFS.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_CFS.eps}  &
%\includegraphics[scale=0.22]{mlp_CFS.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using CfsSubsetEval.}
%\label{conv2CfsSubsetEval}
%\end{figure*}
%
%
%\begin{figure*}[http] 
%\begin{center} 
%\begin{tabular}{ccc}
%\includegraphics[scale=0.22]{m5p_SOM.eps}  &
%\includegraphics[scale=0.22]{lr_SOM.eps}   &
%\includegraphics[scale=0.22]{svm_SOM.eps}  \\
%M5P & LR & SVM 
%\end{tabular}
%\begin{tabular}{cc}
%\includegraphics[scale=0.22]{knn_SOM.eps}  &
%\includegraphics[scale=0.22]{mlp_SOM.eps}  \\
%k-NN & MLP
%\end{tabular}
%\end{center} 
%\caption{Actual VS predicted sale for M5P, LR, SVM, k-NN, MLP models applied on the selected features using SOM analysis.}
%\label{conv2SOM}
%\end{figure*}

%\begin{figure}[!ht] 
%\begin{center}
%  \epsfig{file=fig_time.eps,width=11cm}
%\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As expected, simpler methods are much faster to build the model than the complex ones.}}
%\label{fig:time}
%\end{center}
%\end{figure}

%\begin{figure}[!ht] 
%\begin{center}
%  \epsfig{file=fig_rae.eps,width=11cm}
%\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 8, 7 and 4 features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
%\label{fig:rae}
%\end{center}
%\end{figure}

@@

\section{Example Cases}
\label{example_cases}

@@

Table \ref{Table:special_cases} shows the details of each of the selected editorials.

@@

@@

\subsection{Sales forecasting with all pre-sales features}
\label{subsec:case_sales_all_features}

\begin{table}
\caption{Predicting Total sales for Editorial704}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLU11}

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }

\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

\subsection{Sales forecasting with feature selection}
\label{subsec:case_sales_feature_selection}

>>>>

%In Figures \ref{conv2}, \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} we depict scatter plots for the values of the actual total sales values against the predicted ones obtained by the developed models. 
%Those figures also show the correlation between the two variables and the proportion of variation in actual total sales that is explained by the predicted ones. 
%Figure \ref{conv2} corresponds to the results obtained using all available features without performing any feature selection method. In this figure, it can be noticed that SVM achieved the best results by explaining 88.2\% of the actual values while $k$-NN showed very poor results with only 49.8\%. 
%Figures \ref{conv2ReliefAttributeEval}, \ref{conv2CfsSubsetEval} and \ref{conv2SOM} show same plots after performing ReliefAttributeEval, CfsSubsetEval and SOM feature selection methods, respectively. 
%According to these figures, we can notice that there wasn't almost any significant degradation in the performance of the M5P, LR, SVM and MLP. 
%On the other side, the performance of $k$-NN was dramatically improved after the feature selection process by explaining 84.5\% of variation on average.
%
%

@@

\section{Experiments of special editorial cases}
\label{example_cases}

@@

Table \ref{Table:special_cases} shows number of sold copies and number of titles published by the selected editorials.

@@

The experiments applied on the selected special cases follow the same methodology used previously for the whole dataset. First, the forecasting models are applied on each dataset using all features, then, the three feature selection methods (ReliefAttributeEval, CfsSubsetEval and SOM) are used to reduce the features in each case. Finally, the classification models are applied again on the reduce datasets to evaluate their performance.

\begin{table}
\caption{Predicting Total sales for Editorial704}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 &  $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 88.9 $\pm$0.07 & 71.26 $\pm$21.29  & 125.19 $\pm$50.09  & 39.25 $\pm$11.77  & 47.50 $\pm$15.93  & 0.05 $\pm$0.03\tabularnewline
\hline 
K-NN  & 82.6 $\pm$0.10  & 87.60 $\pm$23.21  & 158.63 $\pm$54.16  & 47.62 $\pm$10.32  & 59.17 $\pm$14.43  & 0.0001 $\pm$0.0003\tabularnewline
\hline 
RF & 87.1 $\pm$0.08  & 74.63 $\pm$22.17  & 139.74 $\pm$54.36  & 40.62 $\pm$10.21  & 52.22 $\pm$16.27  & 0.11 $\pm$0.01\tabularnewline
\hline 
LR  & 83.8 $\pm$0.09  & 97.51 $\pm$18.87  & 155.27 $\pm$45.56  & 54.17 $\pm$13.60  & 60.31 $\pm$21.17  & 0.01 $\pm$0.001\tabularnewline
\hline 
SVM  & 87.4 $\pm$0.07  & 78.74 $\pm$22.25  & 147.30 $\pm$57.99  & 42.43 $\pm$7.83  & 53.29 $\pm$9.35  & 0.06 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLU11}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 77.5 $\pm$0.15  & 573.41 $\pm$192.22  & 860.31 $\pm$456.22  & 58.26 $\pm$15.87  & 66.00 $\pm$29.45  & 0.024 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.2 $\pm$0.16  & 596.62 $\pm$205.37  & 933.06 $\pm$356.11  & 60.62 $\pm$17.85  & 71.36 $\pm$22.34  & 0 $\pm$0.0002\tabularnewline
\hline 
RF & 86.7 $\pm$0.07  & 449.16 $\pm$127.80  & 671.76 $\pm$212.74  & 45.58 $\pm$9.80  & 51.37 $\pm$11.16  & 0.06 $\pm$0.01\tabularnewline
\hline 
LR  & 73.3 $\pm$0.20  & 680.16 $\pm$263.79  & 1103.97 $\pm$850.69  & 69.78 $\pm$27.24  & 86.11 $\pm$71.32  & 0.002 $\pm$0.001\tabularnewline
\hline 
SVM  & 80.4 $\pm$0.12  & 529.35 $\pm$172.50  & 846.01 $\pm$341.12  & 53.26 $\pm$11.92  & 63.54 $\pm$18.25  & 0.03 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDL929 (460752 sales) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 90.0 $\pm$0.10 & 670.24 $\pm$181.05  & 1065.34 $\pm$413.84  & 40.83 $\pm$10.86  & 43.56 $\pm$19.87  & 0.03 $\pm$0.002\tabularnewline
\hline 
K-NN  & 73.3 $\pm$0.19  & 1057.21 $\pm$385.04  & 1875.85 $\pm$916.96  & 61.88 $\pm$12.37  & 68.75 $\pm$15.98  & 0 $\pm$0.0001\tabularnewline
\hline 
RF  & 87.6 $\pm$0.11  & 771.83 $\pm$326.34  & 1490.49 $\pm$930.58  & 45.40 $\pm$14.14  & 55.91 $\pm$31.70  & 0.08 $\pm$0.004\tabularnewline
\hline 
LR  & 86.3 $\pm$0.12  & 922.33 $\pm$289.01  & 1399.84 $\pm$619.62  & 56.11 $\pm$16.17  & 56.43 $\pm$25.09  & 0.005 $\pm$0.001\tabularnewline
\hline 
SVM  & 86.7 $\pm$0.1  & 873.22 $\pm$345.16 & 1621.48 $\pm$985.24  & 50.85 $\pm$11.83  & 57.23 $\pm$20.40  & 0.04 $\pm$0.016\tabularnewline
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Predicting Total sales for Editorial-UDLW12 (2635 sales) }
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
\hline 
M5P  & 83.2 $\pm$0.24  & 14.18 $\pm$6.62  & 23.82 $\pm$11.86  & 43.41 $\pm$20.39  & 55.79 $\pm$30.47  & 0.009 $\pm$0.002\tabularnewline
\hline 
K-NN  & 79.3 $\pm$0.24 & 15.34 $\pm$8.71  & 26.57 $\pm$16.64  & 46.20 $\pm$23.77  & 60.09 $\pm$35.21  & 0.0001 $\pm$0.0002\tabularnewline
\hline 
RF & 85.8 $\pm$0.17  & 14.19 $\pm$6.69  & 23.57 $\pm$11.83  & 42.53 $\pm$16.80  & 53.30 $\pm$23.41  & 0.03 $\pm$0.004\tabularnewline
\hline 
LR  & 82.1 $\pm$0.25 & 14.62 $\pm$7.92  & 24.79 $\pm$15.08  & 44.57 $\pm$24.27  & 56.85 $\pm$35.07  & 0.002 $\pm$0.0005\tabularnewline
\hline 
SVM  & 83.5 $\pm$0.21  & 14.01 $\pm$7.61  & 25.61 $\pm$15.30  & 40.66 $\pm$16.03  & 53.28 $\pm$18.45  & 0.02 $\pm$0.02\tabularnewline
\hline 
\end{tabular}
\end{table}

@@

%\subsection{Sales forecasting with feature selection}
%\label{subsec:case_sales_feature_selection}
